%\usepackage[pdftex]{hyperref}

\documentclass[10pt]{article}
%\documentclass[10pt,twocolumn]{article}

% Set left margin - The default is 1 inch, so the following 
% command sets a 1.25-inch left margin.
\setlength{\oddsidemargin}{-0.5in}
%\setlength{\evensidemargin}{-0.25in}

% Set width of the text - What is left will be the right margin.
% In this case, right margin is 8.5in - 1.25in - 6in = 1.25in.
\setlength{\textwidth}{7in}
%\setlength{\textwidth}{6.5in}

% Set top margin - The default is 1 inch, so the following 
% command sets a 0-inch top margin.
\setlength{\topmargin}{-1in}

% Set height of the text - What is left will be the bottom margin.
% In this case, bottom margin is 11in - 0.75in - 9.5in = 0.75in
\setlength{\textheight}{9.5in}

% Set the beginning of a LaTeX document
\begin{document}

\begin{center}
  %\begin{tabular}{lr}
  \begin{tabular*}{7.5in}{l@{\extracolsep{\fill}}r}
		\bf{\sc{\huge{David Michael}}} & Daytime: (505) 845-9113\\
		13209 Bellamah Ave. NE & Evening: (505) 550-9296\\
		Albuquerque, NM 87112 & dave.a.michael@gmail.com\\
		\hline
	\end{tabular*}
\end{center}

\subsection*{OBJECTIVE:}  A software engineering position developing challenging, impactful technology in a team environment.

\subsection*{WORK EXPERIENCE}

\noindent
\begin{tabular*}{7in}{l@{\extracolsep{\fill}}r}
\textbf{Sandia National Laboratories} & June 2001 - Present\\
Senior Member of the Technical Staff &\\
\end{tabular*}
\begin{itemize}
\begin{item}
\textbf{Principal Investigator}, Laboratory Directed Research and Development Project (present)
\\
Currently leading a research team seeking to improve the state of the art of real-time, online scheduling algorithms for remote sensing systems.
\end{item}
\begin{item}
\textbf{Implementation Architect}, ICADS Build 6 (present)
\\
Acting as Implementation Architect for ICADS Build 6, which is a large multi-year software project to provide the ground station software for the United States Nuclear Detonation Detection System.
  \begin{itemize}
	\begin{item}
	Coordinate interactions between Architecture team, Tools team, and Development teams.
	\end{item}
        \begin{item}
        Aid developers with design, coding, and testing.
        \end{item}
	\begin{item}
	Led adoption of automated nightly unit testing.
        \end{item}
        \begin{item}
        Evaluated static analysis tools and will lead integration of the selected tool. 
	\end{item}
	\begin{item}
	Defined unit testing guidelines and code review process; maintained design and coding guidelines.
	\end{item}
  \end{itemize}
\end{item}

\begin{item}
\textbf{Principal Investigator}, Net-Centric Prototype.
\\
Led a small team which developed a real-time geospatial information system using Google Earth.
\begin{itemize}
  \begin{item}
    Presented demo and findings to management and authored a white paper describing the findings in detail.
  \end{item}
  \begin{item}
    Increased understanding and adoption of web service technologies for future defense and intelligence programs at Sandia.
  \end{item}
\end{itemize}
\end{item}

\begin{item}
\textbf{Software Engineer}, ICADS Build 5.
\\
Designed, developed, and maintained a number of low-level subsystems critical to ICADS Build 5 (predecessor to Build 6), with customers throughout the project.
\begin{itemize}
	  \begin{item}
	    Applied template metaprogramming techniques to simplify and optimize container class serialization, and improve callbacks.
	  \end{item}
	  \begin{item}
	    Trained the development team on exception-safe programming, including the use of the RAII idiom and commit-and-rollback semantics.
	  \end{item}
	  \begin{item}
	    Designed and implemented a persisted, distributed Observer Pattern; a critical component of the software architecture.
	  \end{item}
	  \begin{item}
	    Made major improvements to the custom interprocess-communication framework, including enhancing reliability, throughput, and scalability.
	  \end{item}
\end{itemize}
\end{item}

\end{itemize}

\subsection*{EDUCATION}
\begin{itemize}
\begin{item}
	\textbf{M.Eng. in Computer Science}, Cornell University 2006\\
	4.09 GPA (A = 4.0, A+ = 4.3)\\
  Relevant Coursework:  Design and Analysis of Algorithms, Empirical Methods in Machine Learning, Advanced Methods in Machine Learning, Structure of Information Networks.
\\
	Projects:
	\begin{itemize}
		\item{Developed a novel web search algorithm combining link and content information.  Implemented and demonstrated the algorithm using complete wikipedia data.}
		\item{Developed a variation on the ``Stacking'' ensemble learning method using the concept of model bagging from the Ensemble Selection algorithm.}
		\item{Applied graph cut energy minimization to the problem of white matter tractography using diffusion tensor imaging.}
                \item{Implemented ensemble selection in Weka open source machine learning suite.}
	\end{itemize}
\end{item}
\begin{item}
	\textbf{B.S. in Computer Science} (Mathematics minor), Denison University 2001\\
	Overall GPA 3.79, Major GPA 3.98 (Summa Cum Laude)\\
Relevant Coursework:  Algorithms and Data Structures, Operating Systems, Networking, Discrete and Combinatorial Mathematics, Artificial Intelligence, Programming Languages
\end{item}  
\end{itemize}

\subsection*{SKILLS}
\begin{itemize}
	\begin{item}
	C++, Python, Java, Perl, C, BASH Scripting
	\end{item}
	\begin{item}
	Machine Learning/Data Mining
	\end{item}
	\begin{item}
	Object-Oriented Design \& Development, Design Patterns
	\end{item}
	\begin{item}
	Distributed Computing \& Network Programming (CORBA, Sockets, Web Services)
	\end{item}
	\begin{item}
	Concurrent Programming (shared memory and message passing)
	\end{item}
	\begin{item}
	Generic programming and template metaprogramming
	\end{item}

	\begin{item}
	Linux, Solaris, Windows, Mac OS X
	\end{item}
	\begin{item}
	UML, Rational Software Architect, Rational Rose
	\end{item}
	\begin{item}
	dbx, gdb, Sun collect/analyze, Purify, Quantify
	\end{item}
	\begin{item}
	Eclipse, vi, SlickEdit, NetBeans, Visual Studio 
	\end{item}
	\begin{item}
	Klocwork Insight, Coverity Prevent (Static analysis)
	\end{item}
\end{itemize}
%\newpage
\noindent

%\large{\textbf{Miscellaneous}}
\subsection*{MISCELLANEOUS}
\begin{itemize}
	\item{Sandia Employee Recognition Award, ICADS project, 2006.}
        \item{Several Sandia SPOT awards for individual technical achievements.}
	\item{Contributor to TAO, an open-source C++ CORBA implementation.}
	\item{Contributor to Weka, a Java open-source machine learning suite.}
	\item{Upsilon Pi Epsilon, Pi Mu Epsilon (Computer Science and Mathematics honoraries)}
	\item{Member of winning team at Denison University's spring programming contest in 2000 and 2001.}
	\item{Lead singer and guitar player for local Albuquerque band ``void*''}
\end{itemize}
\subsection*{References}
\begin{itemize}
	\item{\textbf{Sean Stroud}, ICADS Lead Architect, Sandia National Laboratories:  \textbf{ststrou@sandia.gov}}
	\item{\textbf{John Ball}, ICADS Architect, Sandia National Laboratories:  \textbf{jrball@sandia.gov}}
	\item{\textbf{Rich Caruana}, Cornell University:  \textbf{caruana@cs.cornell.edu}}
\end{itemize}
\end{document}
